pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Pretend that create_all_experiments can exlude one inference model as shown in https://github.com/richelbilderbeek/pirouette/issues/227

In the previous research question we have seen how to use \verb;pirouette; to  
run the analysis on main pipeline, either using a 'generative' or a 
'best\_candidate' inference model. We also saw that to exclude the baseline 
error due to stochasticity it is possible to run a parallel twin pipeline. In 
this way two error distributions are obtained. Comparing them it is possible to 
estimate the error made by BEAST2 when inferring a posterior distribution 
starting from a phylogeny generated under an unknown generative tree prior.
We can sum up all \verb;pirouette;'s features presented so far in the fifth 
research question:

@@

In this example, we use a tree generated by the Yule process.
Instead of using the common Yule tree as in example 1, we'll use
a Yule tree of low (actually: zero) likelihood: 
the one as used in examples 2-4.
by using the code shown in listing~\ref{lst:unknown_phylogeny}.
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
generative_experiment <- create_experiment(
  model_type = "generative",
  run_if = "always",
  do_measure_evidence = TRUE
)
\end{lstlisting}

Specifying all candidates can be done simply by calling 
\verb;create_all_experiments;. In this case, all candidates will use the same 
site and clock model, and only differ in their tree priors:

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
candidate_experiments <- create_all_experiments(
  site_models = list(create_jc69_site_model()),
  clock_models = list(create_strict_clock_model()),
  tree_priors = list(
    create_bd_tree_prior(), 
    create_ccp_tree_prior(), 
    create_cep_tree_prior()
  )
)
\end{lstlisting}

>>>>

In ERQs 1 and 2 we used \verb;pirouette; to  
run the analysis on the main pipeline, either using a 'generative' or a 
'best\_candidate' inference model, resulting in one error distribution,
that does not mean much on its own.
In ERQs 3 and 4 we measure the baseline error caused by stochasticity,
by running a parallel twin pipeline, resulting in two error distributions:
the baseline error and the complete inference error.
We can sum up all \verb;pirouette;'s features presented so far in the fifth 
research question:

@@

In this example, we use a tree generated by the Yule process.
Instead of using the common Yule tree as in example 1, we'll use
a Yule tree of low (actually: zero) likelihood: 
the one as used in ERQs 2-4, by using the code shown 
in listing~\ref{lst:unknown_phylogeny}.
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
generative_experiment <- create_experiment(
  inference_conditions = create_inference_conditions(
    model_type = "generative",
    run_if = "always",
    do_measure_evidence = TRUE
  )
  inference_model = create_inference_model(
    site_model = create_jc69_site_model(),
    clock_model = create_strict_clock_model(),
    tree_prior = create_yule_tree_prior()
  )
)
\end{lstlisting}

Specifying all candidates can be done simply by calling 
\verb;create_all_experiments; and excluding the generative inference model,
resulting in 39 candidate experiments:

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
candidate_experiments <- create_all_experiments(
  exclude_model = generative_experiment$inference_model
)
\end{lstlisting}
